{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion}

### 2017-01-04 proposal/thesprop.tex
dates and committe members
quicksand verif
cuidado...
timeline

% some useful packages
\usepackage{times}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[charter]{mathdesign}
\usepackage[numbers,sort]{natbib}
\usepackage[backref,pageanchor=true,plainpages=false, pdfpagelabels, bookmarks,bookmarksnumbered,
%pdfborder=0 0 0,  %removes outlines around hyper links in online display
]{hyperref}
\usepackage{subfigure}
\usepackage[linesnumbered,ruled]{algorithm2e}
\usepackage{algpseudocode}

@@

@@

\title{ %% {\it \huge Thesis Proposal}\\
{\bf Practical Concurrency Testing} \\
\normalsize \vspace{1em}
{\em or, How I Learned to Stop Worrying and Love the Exponential Explosion}}
\author{Ben Blum}
\date{Janucember 2016}
\Year{2016}
\trnumber{}

\committee{
Garth Gibson, Chair \\
David A. Eckhardt \\
Yet another person \\
Someone from a strange and faraway land
}

@@

Stateless model checking is a powerful technique for testing concurrent programs,
capable in theory of rooting out any bug or providing total verification on any program,
but suffers several problems which relegate that theory to fantasy land \cite{vargomax}.
Chief among those problems is exponential explosion of state spaces,
making it difficult to decide in advance which combinations of preemption points can be productively tested within a given time limit.
Another major problem is the manual annotation effort required to test certain types of concurrent programs,
which is especially relevant for operating systems students who implement their own kernels.
In this document I have proposed a thesis which will solve both problems.
I leave you now with a proposed timeline for bringing each project to fruition.

\begin{itemize}
	\item TODO % TODO
\end{itemize}

>>>>

% some useful packages
\usepackage{times}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage[charter]{mathdesign}
\usepackage[numbers,sort]{natbib}
\usepackage[backref,pageanchor=true,plainpages=false, pdfpagelabels, bookmarks,bookmarksnumbered,
%pdfborder=0 0 0,  %removes outlines around hyper links in online display
]{hyperref}
\usepackage{subfigure}
\usepackage[linesnumbered,ruled]{algorithm2e}
\usepackage{algpseudocode}

@@

\newtheorem{theorem}{Theorem}

\newcommand\llama[1]{\includegraphics[width=#1]{llama.pdf}}
\newcommand\llitem{\item[\llama{1em}]}

@@

\title{ %% {\it \huge Thesis Proposal}\\
{\bf Practical Concurrency Testing} \\
\normalsize \vspace{1em}
{\em or, How I Learned to Stop Worrying and Love the Exponential Explosion}}
\author{Ben Blum}
\date{January 2017}
\Year{2017}
\trnumber{}

\committee{
Garth Gibson, Chair \\
David A. Eckhardt \\
Brandon Lucia \\
Haryadi Gunawi (University of Chicago)
}

@@

Stateless model checking is a powerful technique for testing concurrent programs,
capable in theory of rooting out any bug or providing total verification on any program,
but suffers several problems which relegate that theory to fantasy land \cite{vargomax}.
Chief among those problems is exponential explosion of state spaces,
making it difficult to decide in advance which combinations of preemption points can be productively tested within a given time limit.
Another major problem is the manual annotation effort required to test certain types of concurrent programs,
which is especially relevant for operating systems students who implement their own kernels.
In this document I have proposed a thesis which will solve both problems.

I leave you now with a proposed timeline for bringing each project to fruition.
Bear in mind that for the first half of 2017, I'll be working with a full-time research assistant,
David Vernet, on the transactional memory and porting Landslide projects.

\begin{itemize}
	\item 2017 January: Submit thesis proposal, begin work on TM project (Section~\ref{sec:tm}). Also submit revised IRB proposal for planned user studies.
	\item 2017 ???uary: Present thesis proposal (whenever the committee is free).
	\item 2017 February: Develop ``grading'' TA user study and deploy it in 15-410 (Section~\ref{sec:grading}).
	\item 2017 March-April: Finish implementation/evaluation of TM; write a paper about it.
	\item 2017 April-June: Begin ``port Landslide to VMware or Bochs'' project (Section~\ref{sec:pintos-todo}).
	\item 2017 June-July: Resubmit paper about 410 user studies (Section~\ref{sec:studence}) (previously rejected from SIGCSE). Also run ``variance'' Quicksand experiments (Section~\ref{chap:quicksand}).
	\item 2017 August-October: Polish and deploy Pintos user study (Section~\ref{sec:pintos-todo}).
	\item 2017 September-December: Write thesis. Also deploy 410 TA grading study once more for more data.
	\item 2017 December: Defend \& graduate.
\end{itemize}

For pretty much any reason (much like hardware transactions),
I may need to delay the timeline by a semester, defending instead in 2018 June.
For example, the above plan to deploy a Pintos user study within one semester's time of finishing the open-source Landslide port is quite ambitious,
assuming among other things smooth negotiations with the OS course staff at another university.
Anyway, this is my optimistic proposal. Thanks for reading.
